### 2005-11-10 doc/EFA/efa.tex

\noindent \textbf{Proof}: We show this by considering three
automata $A, A'$ and $A''$ and showing that $(A\|A')\|A'' =
A\|(A'\|A'')$.
\newline\newline
\noindent The 8-tuple representing $(A\|A')\|A''$ is
\begin{center}
\begin{tabular}{ll}
  $(A\|A')\|A'' =$ & $\Big \langle (Q \times Q') \times Q'',$\\
  & $ \big(\Sigma \bigcup \Sigma' \big) \bigcup \Sigma'',$\\
  & $\delta^{(A\|A')\|A''},$\\
  & $\big((q_i, q'_i) , q''_i\big),$\\
  & $(Q_m \times Q_m') \times Q_m'',$\\
  & $\big[[X, X'], X'']$\\
  & $G^{(A\|A')\|A''},$\\
  & $\big[[X_m, X'_m], X''_m \big] \Big \rangle$
\end{tabular}
\end{center}

@@

>>>>

\noindent \textbf{Proof}: To prove this associativity we
considering three automata $A, A'$ and $A''$, and show that
$(A\|A')\|A'' = A\|(A'\|A'')$. First, we assume that the three
automata have no common variables.
\newline\newline
\noindent The 8-tuple representing $(A\|A')\|A''$ is
\begin{center}
\begin{tabular}{ll}
  $(A\|A')\|A'' =$ & $\Big \langle (Q \times Q') \times Q'',$\\
  & $ \big(\Sigma \bigcup \Sigma' \big) \bigcup \Sigma'',$\\
  & $\delta^{(A\|A')\|A''},$\\
  & $\big((q_i, q'_i) , q''_i\big),$\\
  & $(Q_m \times Q_m') \times Q_m'',$\\
  & $\big[[X, X'], X'']$\\
  & $G^{(A\|A')\|A''},$\\
  & $\big[[X_m, X'_m], X''_m \big] \Big \rangle$
\end{tabular}
\end{center}

@@

klkljkll
